\huge Tor's Usability for Censorship Circumvention

### 2016-04-14 pets2017-paper/pets2017-paper.tex
remove extra sentence.
Dump a table of completion rates and times into the paper.

The redesigned interface conservatively interacts with users by automating only safe configuration processes and still allowing users to have control over configuring all interacting network components. The design requires more maintenance because of the explicit advice given on which order to select bridges and advice on error messages, which may change as the censorship environments change. For additional changes that can be made and alternate approaches for interacting with the user, see Section~\ref{sec:discussion}.

@@

>>>>

The redesigned interface conservatively interacts with users by automating only safe configuration processes and still allowing users to have control over configuring all interacting network components. The design requires more maintenance because of the explicit advice given on which order to select bridges and advice on error messages, which may change as the censorship environments change.

@@

% This table is generated by info.R.
\begin{tabular}{l r r r r}
& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
\noalign{\hrule}
E1-NEW & 19/19 & 100\% & 0:20 \\
E1-OLD & 19/19 & 100\% & 1:01 \\
E2-NEW & 18/19 & 95\% & 3:22 \\
E2-OLD & 16/19 & 84\% & 4:01 \\
E3-NEW & 13/20 & 65\% & 12:38 \\
E3-OLD & 10/20 & 50\% & 18:16 \\
\end{tabular}
